\textbf{Response Letter}

### 2018-12-24 doc/aij18/major-revision/letter.tex
Updated Dec 24 10.20

@@

\item \textbf{Compilation scheme}. Reviewers \#1 and \#3 show several concerns about the understanding of section 4.4., the compilation approach. We acknowledge their concerns and we have thus introduced an introductory explanatory subsection that explains .......... before going into the technical details. We hope this new subsection will help the reader to have first a broad view of the compilation scheme before diving into the technicalities.
\end{enumerate}

@@

\subsection*{Reviewer \#1}

@@

\textcolor{blue}{We agree with the reviewer that the paper lacks a description of the overall approach. We refer the reviewer to the main modification \#1 exposed above. Following the notes of the reviewer's summary, we have also included a brief summary at the end of the section Introduction that serves to wrap up the main features of \FAMA. Additionally, and as requested by the other reviewers too, we introduced the main modification \#2. In the newly introduced sub-section, we define in detail the problem to solve, which we believe also helps to grasp the overall picture of \FAMA.}

@@

\textcolor{blue}{The reviewer is right in that the definition of effects was confusing. It all stem from the adoption of the open world assumption, which leads to have states containing positive and negative literals, but we did not adapt the definition of effects appropriately. In section 2.1, we have now included a brief explanation of the open world assumption and the representation of states, and we have adapted the definition of effects accordingly.}

@@

\textcolor{blue}{The additional assumptions are the syntactic constrains imposed by \strips\ planning models. We agree with the reviewer that other domain models do not satisfy these assumptions. We intend to extend the compilation scheme to planning models other than \strips\ as future work, but the focus of this paper is exclusively on \strips\ models. We have included a sentence before describing the assumptions to clearly state that they derive from the syntactic constraints of \strips.}

@@

\textcolor{blue}{We have reformulated the explanation of the observability in plan traces of section 2.1 to make it more comprehensible and added a few more details that help distinguish the different cases of observability. We have also highlighted the two special cases, PO* and NO, that derive from PO. With respect to the relation between actions and state partial observability, we refer the reviewer to the main modification \#2 and to section 3 in general. The new section 3.1 ...  Additionally, Table 4 in section 3.2, where all possible combinations are displayed. Particularly, as it is written in the text, the case FO actions with FO states is straightforward because in this case every state is available and so preconditions and effects are derivable by lifting the corresponding literals. The case FO actions with PO* states is a common case handled by some learning approaches as shown in Table 2 of section 2.2.}

@@

@@

@@

@@

@@

@@

@@

\subsection*{Reviewer \#2}

@@

\textcolor{blue}{Following the reviewer's advice, we have substantially changed section 3. We refer the reviewer to our main modification \#2. We removed the complexity table of page 8, focusing now the discussion around the two main cases that determine the difficulty of the learning task and giving an indication of the task complexity according to the characteristics that define these two cases. We also changed the reference and added instead the original work that proves that boolean SAT problems are NP-complete.}

@@

\textcolor{blue}{With respect to the repetition of the definition of a \strips\ action model .... }

@@

\textcolor{blue}{Timeouts are only observed in the setting with NO action sequences and NO state trajectories. We have added a few sentences providing more details on this issue.}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
    Page 1.  "Two different types of data are generally identified in the generation of explanations … (2) data that do not accurately represent the decision-making process because the observed external behavior of the agent responds to a black-box model." -- First, I think you meant "corresponds" and not "responds". Second, if the agent is treated as a black box, then this is not really a way to generate explanation. Please better explain the text after (2) .
\end{mdframed}

\textcolor{blue}{We think the paragraph was rather confusing and that we did not clearly come through our intention to set an analogy between the data sources used in explainable AI and the data required by the learning approaches. For this reason, we have removed the paragraph and included instead a list of planning-related tasks that require a planning model for being solved. We think this rather complete but non-exhaustive list is a pretty good indication of the need for learning planning models.}

@@

\textcolor{blue}{We have rephrased all the paragraphs and sentences pointed by the reviewer. With respect to the first comment, we attempt to make it clear that classical planning techniques can be used to generate a large variety of planning models, not only \strips\ models, and that these techniques underpin some relevant concepts that are also reusable in learning models when the behaviour of the agent is not available.}
\textcolor{blue}{With respect to the other two comments, besides using different expressions to refer to the two concepts, we have included some additional side explanations that we hope help understand the meaning of the sentences.}
\vspace{0.1cm}

@@

\textcolor[rgb]{0.00,0.07,1.00}{We have moved the 4th paragraph of the Related Work, where we commented on the predicates and action headers of the approaches, to the end of the section because it makes more sense to comment on this issue when comparing with LOCM. Also, we clarified the meaning of action header (action name and parameters) because the formal definition of an actio header is actually introduced in section 4.}

@@

\textcolor[rgb]{0.00,0.07,1.00}{We have moved the 4th paragraph of the Related Work, where we commented on the predicates and action headers of the approaches, to the end of the section because it makes more sense to comment on this issue when comparing with LOCM. The reviewer is right in that FAMA also assumes predicates and action headers are provided or otherwise are extractable from the plan traces. We believe it is more appropriate to move this comment after presenting LOCM because LOCM is an exception that learns the predicates using FSM since no observed states are given in the plan trace.}

@@

2.       When talking about LAMP, you write that it allows trajectories up to a "minimum percentage of 1/5 …" – again, is this requirement mandatory in their algorithm, or is it just what they happened to get in their experiments? Also, if you write 1/5 then you should write "ratio" and not "percentage".

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
    Pages 5-7. "… the state of a sort" – what is a "sort"?
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
    Pages 5-7. "As many of the approaches in section 2 assume, there may be an …" – this text is redundant. It just repeats again what was said twice already.
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
  Page 8."… an unbound number of missing actions …" – should be "unbounded'
\end{mdframed}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
  Page 8."When the plan traces is fully observed, learning STRIPS action models is straightforward" – The reference if for work done in 2018, while learning an action model in this setting has been discussed in IJCAI 2017 by Stern and Juba (Safe, model-free learning of action models").
\end{mdframed}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
- "On the other hand, a striking figure …" – I could not understand this sentence.

- "Let $\Omega_v = {v_i}_{i=1}^{max_{a\in A} ar(a)}$ be a new set of objects …" – I think "ar(a)" should be "|ar(a)|"

- "… which is bound to …" – I think should be " which is bounded by"

-          "In more details, for a given …" – delete the "In more details" as you are defining something new, not providing additional details.

-          Please elaborate on the computation of the size of the space of possible STRIPS models.

-          The definition of conditional effects given in 4.3 should be moved to the background section, where you define a STRIPS model.

-          The explanation about the plan prefix and postfix is confusing and not helpful. I recommend removing it. Only after you explain your solution it starts to make sense. Also, I am not sure the term "postfix" is suitable. Maybe "suffix"?

-          The formula for the precondition of apply uses the notation $\Rightarrow$ which was not defined.
\end{mdframed}

-          I'd appreciate more details on the mentioned post-processing, e.g., a pseudo code.

-          At the bottom of the page, you write that VAL cannot address the model validation of a partial model and on the other hand it requires a full plan and full action model. I don't see how this is "on the other hand"? it is the same "hand"
\end{mdframed}

@@

\textcolor{blue}{We have provided better justification for the use of semantic evaluation metrics.}

@@

-          What does it mean that a learned action model is sound and complete?
\end{mdframed}

\textcolor{blue}{The precision and recall metrics give a notion of the soundness and completeness of a model. By a sound model we understand one where all preconditions and effects are correct, either wrt to the GTM or a test set, so there is no need to remove anything. A complete model is one where no precondition or effect is missing.}

-          "… to flaws that appear more than once in the plan traces …" – I recommend to clarify: "flaws in the action model that manifest more than once in the plan traces".

-          "… generated 10 plan traces (each with 10 actions …" – the parenthesis should be removed.
\end{mdframed}

@@

-          "… the horizon of the solution plan is also known. " – how do you know the horizon? You know the length of the given traces, but how do you know how many actions are needed to build the action model?

-          "… a solution plan is solvable in two steps" – which two steps? I thought you put it all in the planner and get both action model and validation in the same step.
\end{mdframed}

@@

-          "… the size of the input knowledge, in the performance …" – should be "on the performance"

-          "… the Precision and Recall" – why capitalized?

-          "By lightening the input constraints …" – maybe "relaxing" instead of "lightening"?
\end{mdframed}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
-          "retain a level of soundness similar to " – what is this "level of soundness"? do you talk about precision?
\end{mdframed}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
  - At the beginning of the evaluation you state the obvious - that the purpose is to evaluate the performance of FAMA and the quality of the models. At this stage to clarify the experimental section I suggest that you indicate, before detailing the set up, what would be success, for example how do you intend to show that your technique is better than or comparable to others? This will no doubt mean introducing the metrics you intend to use and giving an idea of success in terms of them. Also it may mean taking text from the start of the sections 6.2 - 6.5  into the first part of the evaluation section. This will however give a good rational for the 'set-up’, the choice of the particular experimental scenarios, and for the discussion of the results.
\end{mdframed}

>>>>

\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{pstricks}
\usepackage{pst-node}
\usepackage{multirow}
\usepackage{listings}
\usepackage{xspace}

@@

\item \textbf{Compilation scheme}. Reviewers \#1 and \#3 show several concerns about the understanding of section 4.4, the compilation approach. We acknowledge their concerns and we changed section 4 significantly. First, a new introductory paragraph has been added at the beginning of the section so as to provide a rough overview of the compilation approach, making explicit references to the actions that will appear in a plan that solves the planning task that results from the compilation. Second, the explanation of the set of actions that make up the planning task has substantially improved, and we provide concrete examples throughout that will help grasp the target of the three types of actions. We have also changed other minor things (e.g., the first set of actions is now renamed as \textbf{insert actions} instead of program actions) with the purpose to ease a smooth reading.
\end{enumerate}

@@

%##################################################
\subsection*{Reviewer \#1}
%##################################################

@@

\textcolor{blue}{We agree with the reviewer that the paper lacks a description of the overall approach. We refer the reviewer to the main modification \#1 exposed above. Following the notes of the reviewer's summary, we have also included a brief summary at the end of the section Introduction that serves to wrap up the main features of \FAMA. Additionally, and as requested by the other reviewers too, we introduced the main modification \#2. The new section 3 defines the learning task and provides insight of the nature of the problem to solve according to the type of the observed plan trace. We believe that this explanation also helps to grasp the overall picture of \FAMA.}

@@

\textcolor{blue}{The reviewer is right in that the definition of effects was confusing. It all stems from the adoption of the open world assumption, which leads to states that contain positive and negative literals, but we did not adapt the definition of effects appropriately. In section 2.1, we have now included a brief explanation of the open world assumption and the representation of states, and we have adapted the definition of effects accordingly.}

@@

\textcolor{blue}{The additional assumptions are the syntactic constrains imposed by \strips\ planning models. We agree with the reviewer that other domain models do not satisfy these assumptions. We intend to extend the compilation scheme to planning models other than \strips\ as future work, but the focus of this paper is exclusively on \strips\ models. We have included a sentence before the description of the assumptions to clearly state that they derive from the syntactic constraints of \strips.}

@@

\textcolor{blue}{We have reformulated the explanation about the observability in plan traces of section 2.1 to make it more comprehensible and added a few more details that help distinguish the different cases of observability. We have also highlighted the two special cases, PO* and NO, that derive from PO. With respect to the relation between actions and state partial observability, we refer the reviewer to the main modification \#2. The new section 3 presents the combinations of observed state trajectories and
observed action sequences and the impact in the learning task solving. Particularly, as it is written in the text at the end of page 10, the case FO actions with FO states is straightforward because in this case every state is available and so preconditions and effects are derivable by lifting the corresponding literals. The case FO actions with PO* states is a common case handled by some learning approaches as shown in Table 2 of section 2.2. In general, all learning approaches but \FAMA assume FO action sequences, which may come along with PO*, PO or NO state trajectories.}

@@

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ....}}

@@

\textcolor{blue}{Our approach is aimed at learning \strips\ models for classical planning problems $P=\langle F,A,I,G \rangle$ but $P_{\Lambda}=\langle F_{\Lambda},A_{\Lambda},I_{\Lambda},G_{\Lambda} \rangle$, the task that results from the compilation, is modeled as a planning problem with conditional effects. This is the reason why conditional effects are introduced in the compilation scheme since they only intervene in the specification of $P_{\Lambda}$ and do not condition the characteristics of the models that \FAMA is able to learn. Nevertheless, we have now incorporated the explanation about conditional effects within the section 4.2 'Compilation' since this is a merely syntactic aspect of the task formalization.}

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ...  SE SIGUEN CUMPLIENDO LAS SYNTACTIC STRIPS CONSTRAINTS CON CONDITIONAL EFFECTS????? }}

@@

\textcolor{blue}{We refer the reviewer to the main modification \#3. Section 4 has been polished significantly. An introductory paragraph provides a high level description of the approach and examples have been incorporated throughout the text.}

@@

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ... TENEMOS QUE VER ESTO ... }}

@@

\textcolor{blue}{The implications can actually be encoded as a disjunction, as it is the case of the {\tt{\small apply\_stack}} action of Figure 4. The caption of the figure indicates that "implications are coded as disjunctions". The implication of the formula can then be encoded as $\{\neg pre_{p}(\xi) \vee p(\omega)\}_{\forall p\in\Psi_\xi}$.}

@@

\textcolor{blue}{The positions of the validate actions among the apply actions is determined by the planner, which will verify that the state that results after the execution of an apply action comprises the observed state of the plan trace. We have added the following sentence in the document to clarify this point: "There will be a validate action in $\pi_\Lambda$ for every observed state in $\tau$. The position of the validate actions in $\pi_\Lambda$ will be determined by the planner checking that the state resulting after the execution of an apply action comprises the observed state $s_j\in\tau$."}

@@

%##################################################
\subsection*{Reviewer \#2}
%##################################################

@@

\textcolor{blue}{Following the reviewer's advice, we have completely remodeled section 3 and we have introduced major improvements in section 4. We refer the reviewer to our main modifications \#2 and \#3. We removed the complexity table of page 8, focusing now the discussion around the two main cases that determine the difficulty of the learning task and giving an indication of the task complexity according to the characteristics that define these two cases. We also changed the reference and added instead the original work that proves that boolean SAT problems are NP-complete.}

@@

\textcolor{blue}{With respect to the repetition of the definition of a \strips\ action model, conditional effects are introduced in section 4 because these are exclusively used for modeling the task that results from the compilation, $P_{\Lambda}=\langle F_{\Lambda},A_{\Lambda},I_{\Lambda},G_{\Lambda} \rangle$. Nevertheless, we have now incorporated the explanation about conditional effects within the section 4.2 'Compilation' since this is a merely syntactic aspect of the task formalization.}

\textcolor{blue}{With respect to the third observation, we have introduced several changes in section 5. First, we provide the standard definitions of precision and recall at the beginning of the section. Then, we adapt these two concepts to planning problems in Def. 4 and 5, respectively. Subsequently, in section 5.2, we present our novel semantic-based metrics that build upon definitions 4 and 5.}

@@

\textcolor{blue}{As indicated by the reviewer, timeouts are only observed in the setting with NO action sequences and NO state trajectories. We have added a few sentences providing more details on this issue.}

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{SOLO HE VISTO UNA FRASE DE TIMEOUTS SOBRE EL GRID ... Y EL RESTO DE DOMINIOS? NO SE PUEDE DECIR NADA???? }}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
    Page 1.  "Two different types of data are generally identified in the generation of explanations ‚Ä¶ (2) data that do not accurately represent the decision-making process because the observed external behavior of the agent responds to a black-box model." -- First, I think you meant "corresponds" and not "responds". Second, if the agent is treated as a black box, then this is not really a way to generate explanation. Please better explain the text after (2) .
\end{mdframed}

\textcolor{blue}{We think this paragraph was rather confusing and that we did not clearly come through our intention to set an analogy between the data sources used in explainable AI and the data required by the learning approaches. For this reason, we have removed the paragraph and included instead a list of planning-related tasks that require a planning model for being solved. We think this rather complete but non-exhaustive list is a pretty good indication of the need for learning planning models.}

@@

\textcolor{blue}{We have rephrased all the paragraphs and sentences pointed by the reviewer. With respect to the first comment, we attempt to make it clear that classical planning techniques can be used to generate a large variety of planning models, not only \strips\ models, and that these techniques underpin some relevant concepts that are also reusable in learning models when the behaviour of the agent is not available.}

\textcolor{blue}{With respect to the other two comments, besides using different expressions to refer to the two concepts, we have included some additional side explanations that we hope help understand the meaning of the sentences.}
\vspace{0.1cm}

@@

\textcolor[rgb]{0.00,0.07,1.00}{We have moved the 4th paragraph of the Related Work, where we commented on the predicates and action headers of the approaches, to the end of the section since it makes more sense to comment on this issue when comparing with LOCM. Also, we clarified the meaning of action header (action name and parameters) because the formal definition of an action header is actually introduced in section 4.}

@@

\textcolor[rgb]{0.00,0.07,1.00}{The reviewer is right in that \FAMA also assumes that predicates and action headers are provided or otherwise are extractable from the plan traces. We believe it is more appropriate to move this comment after LOCM is introduced since LOCM is an exception that learns the predicates using Finite-State Machines (FSM) because no observed states are given in the plan trace.}

@@

2.       When talking about LAMP, you write that it allows trajectories up to a "minimum percentage of 1/5 ‚Ä¶" ‚Äì again, is this requirement mandatory in their algorithm, or is it just what they happened to get in their experiments? Also, if you write 1/5 then you should write "ratio" and not "percentage".

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
    Pages 5-7. " ... the state of a sort"  -- " what is a "sort"?
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
    Pages 5-7. "As many of the approaches in section 2 assume, there may be an ..."  - this text is redundant. It just repeats again what was said twice already.
\end{mdframed}

\textcolor[rgb]{0.00,0.07,1.00}{We refer the reviewer to the main modification \#2. Section 3 has substantially changed and this sentence does no longer appear in the text.}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
  Page 8." ... an unbound number of missing actions ..."  - should be "unbounded'
\end{mdframed}

\textcolor[rgb]{0.00,0.07,1.00}{Corrected.}

@@

\textcolor[rgb]{0.00,0.07,1.00}{It is true that a machinery for capturing and labeling the executed actions can be deployed. In either case, whether a human or an automated mechanism, the need of a fully observable behaviour of the agent imposes a limitation in learning systems. We have soften the sentence including the word "\emph{commonly}" in our exposition.}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
  Page 8."When the plan traces is fully observed, learning STRIPS action models is straightforward" - The reference if for work done in 2018, while learning an action model in this setting has been discussed in IJCAI 2017 by Stern and Juba (Safe, model-free learning of action models").
\end{mdframed}

@@

\textcolor[rgb]{0.00,0.07,1.00}{We have removed the paragraph regarding the evaluation of the learned models from section 3 and moved to section 5. We also clarify the use of the word "semantic" as requested by another reviewer as well.}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
- "On the other hand, a striking figure ..."  - I could not understand this sentence.
\end{mdframed}

\textcolor[rgb]{0.00,0.07,1.00}{In the remodeling of section 3, the paragraph about the size of the training dataset has been removed too. The ideas presented here have been moved to section 6.}

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ... NO HE VISTO ESTE PARRAFO EN LA SECCION 6, NO PUSISTE ESTA INFORMACION EN 6??}}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
- "Let $\Omega_v = {v_i}_{i=1}^{max_{a\in A} ar(a)}$ be a new set of objects ‚Ä¶" ‚Äì I think "ar(a)" should be "|ar(a)|"
\end{mdframed}

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ...}}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
- "... which is bound to ..."  - I think should be " which is bounded by"
\end{mdframed}

\textcolor[rgb]{0.00,0.07,1.00}{Corrected.}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
- "In more details, for a given ..." - delete the "In more details" as you are defining something new, not providing additional details.
\end{mdframed}

\textcolor[rgb]{0.00,0.07,1.00}{Corrected.}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
- Please elaborate on the computation of the size of the space of possible STRIPS models.
\end{mdframed}

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ...}}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
- The definition of conditional effects given in 4.3 should be moved to the background section, where you define a STRIPS model.
\end{mdframed}

\textcolor{blue}{Our approach is aimed at learning \strips\ models for classical planning problems $P=\langle F,A,I,G \rangle$ but $P_{\Lambda}=\langle F_{\Lambda},A_{\Lambda},I_{\Lambda},G_{\Lambda} \rangle$, the task that results from the compilation, is modeled as a planning problem with conditional effects. This is the reason why conditional effects are introduced in the compilation scheme since they only intervene in the specification of $P_{\Lambda}$ and do not condition the characteristics of the models that \FAMA is able to learn. Nevertheless, we have now incorporated the explanation about conditional effects within the section 4.2 'Compilation' since this is a merely syntactic aspect of the task formalization.}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
- The explanation about the plan prefix and postfix is confusing and not helpful. I recommend removing it. Only after you explain your solution it starts to make sense. Also, I am not sure the term "postfix" is suitable. Maybe "suffix"?
\end{mdframed}

\textcolor[rgb]{0.00,0.07,1.00}{We have introduced a new paragraph at the beginning of section 4 that gives an overview of the compilation approach and explains the two blocks of actions of the solution plan to the learning task. We have reused the concept of "block of actions" to refer to the prefix and postfix of $\pi_{\Lambda}$ in section 4.2 "Compilation".}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
- The formula for the precondition of apply uses the notation $\Rightarrow$ which was not defined.
\end{mdframed}

\textcolor[rgb]{0.00,0.07,1.00}{$\Rightarrow$ is the general logic symbol read as implication. The implications can actually be encoded as a disjunction, as it is the case of the {\tt{\small apply\_stack}} action of Figure 4. The caption of the figure indicates that "implications are coded as disjunctions". The implication of the formula can then be encoded as $\{\neg pre_{p}(\xi) \vee p(\omega)\}_{\forall p\in\Psi_\xi}$ }

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
Pages 15-19.
- I'd appreciate more details on the mentioned post-processing, e.g., a pseudo code.
\end{mdframed}

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ...  SE PUEDE DECIR ALGO MAS O IGNORAMOS EL COMENTARIO?}}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
- At the bottom of the page, you write that VAL cannot address the model validation of a partial model and on the other hand it requires a full plan and full action model. I don't see how this is "on the other hand"? it is the same "hand"
\end{mdframed}

\textcolor[rgb]{0.00,0.07,1.00}{Corrected.}

@@

\textcolor{blue}{We have provided better justification for the use of semantic evaluation metrics in section 5.}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
Pages 15-19.
-  What does it mean that a learned action model is sound and complete?
\end{mdframed}

\textcolor{blue}{The precision and recall metrics give a notion of the soundness and completeness of a model. By a sound model we understand one where all preconditions and effects are correct, either wrt to the GTM or a test set, so there is no need to remove anything. A complete model is one where no precondition or effect is missing. We have added a sentence to clarify this.}

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ...  HE A—ADIDO ESTA FRASE EN EL TEXTO PERO SOLO CON RESPECTO AL GTM. MIRA A VER SI TE PARECE BIEN.}}

@@

- "... to flaws that appear more than once in the plan traces ..." - I recommend to clarify: "flaws in the action model that manifest more than once in the plan traces".

- "... generated 10 plan traces (each with 10 actions ..." - the parenthesis should be removed.
\end{mdframed}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
Pages 15-19.
-  "... the horizon of the solution plan is also known. " - how do you know the horizon? You know the length of the given traces, but how do you know how many actions are needed to build the action model?
\end{mdframed}

\textcolor{blue}{Hopefully the new section 3 (see main modification \#2) helps clarify this question. In a nutshell, sometimes a plan trace indicates the length of the plan (this is the case when SAT solvers can be used) and others it does not (this is the case when planning is required).}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
-  "... a solution plan is solvable in two steps" - which two steps? I thought you put it all in the planner and get both action model and validation in the same step.
\end{mdframed}

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ...  HE A—ADIDO ALGO PARA CLARIFICAR ESTO EN EL TEXTO PERO NO SE SI EST¡ BIEN ... COMPROBAR}}

\textcolor{blue}{Hopefully the new section 3 (see main modification \#2) helps the reviewer clarify this question. }

@@

- "... the size of the input knowledge, in the performance ..." - should be "on the performance"

- "... the Precision and Recall" - why capitalized?

- "By lightening the input constraints ..." - maybe "relaxing" instead of "lightening"?
\end{mdframed}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
-          "retain a level of soundness similar to " ... what is this "level of soundness"? do you talk about precision?
\end{mdframed}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
  - At the beginning of the evaluation you state the obvious - that the purpose is to evaluate the performance of FAMA and the quality of the models. At this stage to clarify the experimental section I suggest that you indicate, before detailing the set up, what would be success, for example how do you intend to show that your technique is better than or comparable to others? This will no doubt mean introducing the metrics you intend to use and giving an idea of success in terms of them. Also it may mean taking text from the start of the sections 6.2 - 6.5  into the first part of the evaluation section. This will however give a good rational for the 'set-up‚Äô, the choice of the particular experimental scenarios, and for the discussion of the results.
\end{mdframed}
